Commutativity of operation-based CRDTs \\ CIS 673 Project Report

### 2020-04-17 report/draft.tex
This is correct. Servois is sound and "relatively complete".

Finally, since Servois is sound, i.e. it never concludes that two
methods commute if they don't, we decided to leave the predicates
empty and gradually extend them if we find that Servois is unable to
give an answer \TODO{Check the validity of the above statement by
  reading the Servois paper}.

>>>>

Finally, since Servois is sound, i.e. it never concludes that two
methods commute if they don't, we decided to leave the predicates
empty and gradually extend them if we find that Servois is unable to
give an answer.
